---
title: "TidyTemplate"
date: 2020-12-22
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_dark())

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-12-22")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

bigmac <- tt$`big-mac`

View(bigmac)

summary(bigmac)

chile <- subset(bigmac, bigmac$name == 'Chile')

bm_ex_data <- bigmac %>%
  select(date, name, local_price, dollar_price) %>%
  mutate(bm_ex_rate = dollar_price / local_price)

bm_ex_data

smalldata <- subset(bm_ex_data, bm_ex_data$name == 'Chile' | bm_ex_data$name == 'Hungary' | bm_ex_data$name == 'Indonesia' | bm_ex_data$name == 'Japan' | bm_ex_data$name == 'South Korea')

smalldata

smalldata2 <- subset(bigmac, bm_ex_data$name == 'Chile' | bm_ex_data$name == 'Hungary' | bm_ex_data$name == 'Indonesia' | bm_ex_data$name == 'Japan' | bm_ex_data$name == 'South Korea')

smalldata2
  


```
Lets observe the countries with the smallest big mac exchange rates (>e-0.2)

```{r Visualize}

smalldata %>%
  ggplot(aes(date, bm_ex_rate)) +
  geom_point() +
  facet_wrap(vars(name))

```
Now lets look at their raw index relative to the US dollar

``` {r Vizualize}

smalldata2 %>%
  ggplot(aes(date, usd_raw)) +
  geom_point() +
  facet_wrap(vars(name))

```
As suspected, each of these countries has an either negative or extremely low raw index. 


```{r Analysis}

bigmac %>%
  ggplot(aes(gdp_dollar, dollar_price)) +
  geom_point() + 
  facet_wrap(vars(name))

bigmac.lm <- lm(gdp_dollar~dollar_price, data=bigmac)

summary(bigmac.lm)

new.data = data.frame(dollar_price=3.5)

predict(bigmac.lm, newdata=new.data)

```
# This tells us that if the big mac price in dollars is $3.50, the gdp per person of the country is $23,865.95. 

``` {r Analysis}

chile %>%
  ggplot(aes(gdp_dollar, dollar_price)) +
  geom_point()

chile.lm <- lm(gdp_dollar~dollar_price, data=chile)

summary(chile.lm)

new.data = data.frame(dollar_price=4)

predict(chile.lm, newdata = new.data)

predict(chile.lm, newdata = new.data, interval = "predict")

cor.test(chile$gdp_dollar, chile$dollar_price, method = 'pearson')

```
This shows us that when looking at chile, it is difficult to make accurate predictions of gdp per person based off the price of a big mac in dollars. These two variables are not significant with one another after looking at the results from the pearson correlation test. 
 
```{r Analysis}

chile %>%
  ggplot(aes(gdp_dollar, local_price)) +
  geom_point()

chile.lm2 <- lm(gdp_dollar~local_price, data=chile)

summary(chile.lm2)

new.data = data.frame(local_price=2600)

predict(chile.lm2, newdata = new.data)

predict(chile.lm2, newdata = new.data, interval = "predict")

cor.test(chile$gdp_dollar, chile$local_price, method = 'pearson')

```
This also shows that in chile, it is still difficult to make accurate predictions on gdp per person based off the price of a big mac in pesos. These two variables are not significant with one another after looking at the results from the pearson correlation test. 



# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
