---
title: "TidyTemplate"
date: 2021-06-22
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(ggbump)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-06-22")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

parks <- tt$parks

View(parks)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

# Remove extra characters from interprettable data points & convert to double data types

parks <- parks %>% 
  mutate(park_pct_city_data = as.double(gsub("%", "", as.character(park_pct_city_data))),
         pct_near_park_data = as.double(gsub("%", "", as.character(pct_near_park_data))),
         spend_per_resident_data = as.double(gsub("\\$", "", as.character(spend_per_resident_data))))

# Lets only look at all North Carolina Cities

nc_cities <- c("Raleigh", "Durham", "Charlotte", "Greensboro", "Winston-Salem", "Charlotte/Mecklenburg County")

nc_parks <- parks %>% 
  filter(city %in% nc_cities)

nc_parks <- nc_parks %>%
  mutate(city = str_replace(city, "Charlotte/Mecklenburg County", "Charlotte"))

View(nc_parks)

# Think of Visualizations to create for NC!

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

# Here we are observing the changes in city rank over time, Raleigh is consistently the best in NC with Charlotte falling off in a major way. Winston-Salem seems to be improving slowly. 

nc_parks %>% 
  ggplot(aes(as.factor(year), spend_per_resident_data, group = city,
             fill = city)) +
  geom_col(position = "dodge") + 
  geom_text(aes(label = rank), vjust = 0, position = position_dodge(width = 1), size = 3) +
  theme_dark() +
  scale_fill_brewer(palette="Oranges") +
  labs(x = "Year", y = "Spending per person ($)", title = "NC spending per person over time", subtitle = "Each column is topped with the city's TPL rank from that year.", fill = "City",
       caption = "Notice Winston-Salem's increase in $ per person and rank over the last 5 years.")


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "NC TPL spending over time.png",
  device = "png")

```
