---
title: "TidyTemplate"
date: 2021-01-05
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
theme_set(theme_dark())
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-01-05")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

```{r}
transit <- tt$transit_cost

head(transit)

transit %>%
  count(country) %>%
  arrange(desc(n))

transit %>%
  filter(country %in% c("US", "CN", "UK", "CN")) %>%
  select(country, city, length, tunnel, tunnel_per, cost_km_millions) %>%
  arrange(desc(cost_km_millions))


transit %>%
  filter(country %in% c("US", "IN", "CN")) %>%
  ggplot(aes(city, cost_km_millions)) +
  geom_col(aes(fill = country)) +
  coord_flip()


transit %>%
  filter(country %in% c("US", "CN", "IN")) %>%
  ggplot() +
  geom_point(aes(stations, cost_km_millions, color = country))
```

Lets take a look at the average cost per kilometer in US millions, only look at the countries with costs over $250,000,000. 

```{r}
transit %>%
  group_by(country) %>%
  summarise(avg_cost_km_mil = mean(cost_km_millions, na.rm = TRUE)) %>%
  filter(avg_cost_km_mil > 250) %>%
  ggplot() +
  geom_col(aes(country, avg_cost_km_mil, color = country), na.rm = TRUE) +
  coord_flip() +
  theme(legend.position = 'none') +
  labs(x = "Country", y = "Average cost per kilometer (in US millions)", title = "On average which three countries spend the most per kilometer?", subtitle = "Answer: USA, SG (Singapore), and NZ (New Zealand)")
```

Now lets take a look at the average line length in KM and lets look at the lines that were less than 10 kilometers.

```{r}
transit %>%
  group_by(country) %>%
  summarise(avg_length = mean(length, na.rm = TRUE)) %>%
  filter(avg_length < 10) %>%
  ggplot() +
  geom_col(aes(country, avg_length, color = country)) +
  coord_flip() +
  theme(legend.position = 'none') +
  labs(title = "Which country has the lowest average line length?", subtitle = "Answer: DE (Germany)", x = "Country", y = "Average Line Length (in km)")

```

Now lets look and see if we have some of the same countries in each of the above two visualizations
```{r}
transit %>%
  group_by(country) %>%
  summarise(avg_length = mean(length, na.rm = TRUE),
            avg_cost_km_mil = mean(cost_km_millions, na.rm = TRUE)) %>%
  filter(avg_length < 10, avg_cost_km_mil > 250) %>%
  ggplot(aes(avg_length,avg_cost_km_mil)) +
  geom_col() +
  geom_text(aes(label = country, color = country)) +
  xlim(2, 10) +
  theme(legend.position = 'none')  +
  labs(title = "Top ten countries that spend the most (US Millions) per km", caption = "Notice that all of these countries have an average of less than 10km per transit line. Why are they all spending so much money?", x = "Average line length (in Km)", y = "Average cost per km (in US millions)")

```
Check out the prices that the US and New Zealand are paying per kilometer, that is crazy for how small their average line is!

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}



```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "1-5-21_image.png",
  device = "png")

```
