---
title: "TidyTemplate"
date: 2021-06-08
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-06-08")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
fishing <- tt$fishing

fishing <- fishing %>% 
  mutate(across(where(is.character), as.factor),
         species = str_replace(str_to_title(species), "([^s])s$", "\\1"))


fishing %>% 
  group_by(species) %>% 
  summarise(value = sum(values, na.rm = TRUE)) 

sum_fish <- function(tbl){
  
  tbl %>% 
  summarise(n_obs = n(),
    value = sum(values, na.rm = TRUE)) %>% 
  arrange(desc(value))
  
} 

# The above code determines the fish that has been produced the most (to the nearest thousand pounds)

fishing %>%  
  group_by(year, species) %>% 
  sum_fish()
```

```{r}

fishing %>%
  group_by(lake, species, year) %>%
  filter(year > 1989 && year < 2000) %>% 
  sum_fish() %>% 
  summarize(total_prod = round(sum(value), 0), 
            best_year = year[which.max(total_prod)]) %>% 
  arrange(-total_prod) %>% 
  ggplot(aes(best_year, total_prod, fill = lake)) +
  geom_col() +
  scale_y_log10() +
  scale_x_continuous(breaks = seq(1990, 2000, 1)) +
  scale_fill_brewer(palette="Spectral") +
  labs(x = "Year", y = "Total Production (to the nearest thousand pounds)",
       fill = "Great Lake", title = "Great Lakes fish production throughout the '90s") +
  theme_dark()

```

```{r}

fishing %>% 
  group_by(species, year) %>% 
  filter(year > 1989 && year < 2000) %>% 
  sum_fish()  %>%
  head(56) %>% 
  ggplot(aes(year, value, fill = species)) +
  geom_col() +
  facet_wrap(~ species) +
  scale_x_continuous(labels = c("90", "91", "92", "93", "94", "95", "96", "97", "98", "99", "00"),
                     breaks = seq(1990, 2000, 1)) +
  scale_fill_brewer(palette = "Set3") +
  theme_dark() +
  theme(legend.position = "none") +
  labs(x = "Year", y = "Total Production (to the nearest thousand pounds)", 
       title = "Highest produced fish in the Great Lakes during the '90s")


```


```{r}

fishing %>%
  group_by(species) %>% 
  sum_fish() %>% 
  head(5) %>% 
  ggplot(aes(x = "", y = value, fill = species)) +
  geom_bar(width = 1, stat = "identity", color = "black") +
  geom_text(aes(label=paste(species, round(value, 0), sep = "\n")), position = position_stack(vjust = 0.5)) +
  coord_polar("y", start = 0) +
  scale_fill_brewer(palette = "YlOrRd") +
  theme_void() +
  theme(legend.position = "none") + 
  labs(title = "Top 5 fish produced across all Great Lakes",
       subtitle = "Number under species name equals thousand lbs produced")

```

```{r}

# Practicing Anova Tests. First performing a test to determine which means test to run. 

anova_practice <- fishing %>% 
  group_by(lake) %>% 
  filter(species == "Lake Whitefish") %>% 
  summarise(n_obs = n(), 
            tot_prod = sum(values, na.rm = TRUE),
            avg_per_lake = mean(values, na.rm = TRUE),
            sd_per_lake = sd(values, na.rm = TRUE))

# Hypo Statement: 
# HO: sigma_mich / sigma_hur = 1 
# HA: sigma_mich / sigma_hur != 1

f <- anova_practice$sd_per_lake[3] / anova_practice$sd_per_lake[2]

f

p <-  2 * pf(f, anova_practice$n_obs[3] - 1, anova_practice$n_obs[2] - 1, lower.tail = F)

p

# p < 0.05 -> Reject H0. Perform the TSHT assuming unequal variances.

# Function to calculate the degrees of freedom for TSHT - Unequal variances

unequal_var_df <-  function(sd_1, sd_2, n_1, n_2) {
  
  df <- (((sd_1^2/n_1)+(sd_2^2/n_2))^2/(((sd_1^2/n_1)^2/(n_1 - 1))+((sd_2^2/n_2)^2/(n_2 - 1))))
  
  return(df)
  
}

# We think that the Lake Whitefish is produced more in Lake Michigan than in Lake Huron.
# Lets test this hypothesis and find out!

# Hypo Statement:
# HO: avg_mich - avg_hur <= 0
# HA: avg_mich - avg_hur > 0

t <- (anova_practice$avg_per_lake[3] - anova_practice$avg_per_lake[2]) / sqrt((anova_practice$sd_per_lake[3]^2/anova_practice$n_obs[3])+(anova_practice$sd_per_lake[2]^2/anova_practice$n_obs[2]))

t

df <- unequal_var_df(anova_practice$sd_per_lake[3], anova_practice$sd_per_lake[2], anova_practice$n_obs[3], anova_practice$n_obs[2])

df

p <- pt(t, df, lower.tail = F)

p # p < 0.0005 -> Reject HO. There is sufficient evidence to suggest that the Lake Whitefish is on average produced more from lake Michigan than from Lake Huron. 
  
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "Production throughout the nineties.png",
  device = "png")

```
